Sea: A hierarchical filesystem for Big-Data Scientific Computing

### 2020-07-23 paper/paper.tex
some comments on the paper
changes to flusher and launch script and minor updates to paper

\begin{document}
\title{Sea: A hierarchical filesystem for processing Big Neuroimaging Data on HPC}

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{N}{euroimaging} datasets have significantly grown in size in the past decade,
resulting in Petabytes of data. As a result, processing pipelines have now shifted from compute to 
data intensive. Some efforts have been made to reduce the data transfer costs in neuroimaging by
introducing new methods to generate pipelines, such as through the adoption of Big Data frameworks
like Apache Spark \cite{Spark} for the pipeline definition \cite{thunder} \cite{other papers}. 
However, such pipelines would have to be entirely rewritten for the framework of choice and Big Data
frameworks like Spark and Dask were found to be difficult to use in describing neuroimaging pipelines \cite{mehta}.
Furthermore, the neuroimaging community relies heavily on the use of well-established command-line tools \cite{fsl, afni, freesurfer}, resulting in
data transfers being inevitable, even with a Big Data framework.

@@

@@

\subsection{Lustre}
\subsubsection{Burst Buffers}
\subsubsection{Other Luster optimizations}
\subsection{Big Data Frameworks and File systems}
HDFS Alluxio Hadoop Spark Dask
\subsubsection{What are they/how do they work}
\subsubsection{Why are the suboptimal for neuroimaging/on HPC}
\subsection{The linux page cache}
\subsubsection{What is it/how does it work}
\subsubsection{Why do we still need Sea}
\subsection{File System implementations}
\subsubsection{Kernel-space file systems}
\subsubsection{FUSE}
\subsubsection{System call interception with ptrace}
\subsubsection{LD\_PRELOAD}

>>>>

\begin{document}
\title{Sea: A hierarchical filesystem for Big-Data Scientific Computing}
% remove neuroimaging and replace with scientific computing  add user-space, switch HPC to computing clusters

@@

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{S}{cientific} computing comes with a unique set of constraints. Such
applications may be composed of heterogeneous workflows, with tasks individual tasks
varying from data to compute intensive, and are typically executed on
shared High Performance Computing (HPC) infrastructure. Scientific applications may consist
of a series of well-established tools. These tools may have initially been developed at
a time when Big Data played a less important role in Scientific computing, and are now
paying a penalty as the amount of data has vastly increased in size. Significant effort

datasets have significantly grown in size in the past decade,
resulting in Petabytes of data. As a result, processing pipelines have now shifted from compute to 
data intensive. Some efforts have been made to reduce the data transfer costs in neuroimaging by
introducing new methods to generate pipelines, such as through the adoption of Big Data frameworks
like Apache Spark \cite{Spark} for the pipeline definition \cite{thunder} \cite{other papers}. 
However, such pipelines would have to be entirely rewritten for the framework of choice and Big Data
frameworks like Spark and Dask were found to be difficult to use in describing neuroimaging pipelines \cite{mehta}.
Furthermore, the neuroimaging community relies heavily on the use of well-established command-line tools \cite{fsl, afni, freesurfer}, resulting in
data transfers being inevitable, even with a Big Data framework.

@@

% add need for userspace / intelligent pipeline flushing
% there is no one-size fits all with data intensive applications
% due to io patterns, so we decided with userspace.

@@

% add related work section
\subsection{Lustre}
% change lustre to shared filesystem
\subsubsection{Other Luster optimizations}
\subsection{Big Data Frameworks and File systems}
HDFS Alluxio Hadoop Spark Dask
\subsubsection{What are they/how do they work}
\subsubsection{Why are the suboptimal for neuroimaging/on HPC}
\subsection{The linux page cache}
\subsubsection{What is it/how does it work}
\subsubsection{Why do we still need Sea}
\subsection{File System implementations}
\subsubsection{Kernel-space file systems}
\subsubsection{Burst Buffers}
\subsubsection{Unionfs}
\subsubsection{FUSE}
\subsubsection{System call interception with ptrace}
\subsubsection{LD\_PRELOAD}
xtreemfs/xtreemos
